---
title: "Day5_Comp_1"
format: 
    html:  
    code-fold:  true
    code-summary: "Show me the code"
editor: visual 
execute: 
  echo : true
  warning: false 
---

### Computation 1 Day 5

```{r}
library(tidyverse)
```

# Explore Star Wars Dataset

-   look at first 6 lines of starwars

-   find the dimensions of starwars

-   make a histogram of character heights

-   make a scatterplot of height vs weight

-   stage, commit, push! check and see changes are safely stored

```{r}
head(starwars)
```

```{r}
dim(starwars)
```

```{r}
ggplot(data = starwars, aes(x=height)) +
  geom_histogram(colour ="red")
```

```{r}
#always check render to see if warnings etc. show up when rendered 
ggplot(data = starwars, aes(x = height, y = mass)) +
  geom_point(colour = "blue",size = 1)
```

-   starwars\$height, gives a vector of VALUES

# Calculate Summary Statistics 

-   mean() function to find means (better for symmetric data)

-   use sd() function to find standard deviations (better for symmetric data, skewed data use median)

```{r}
#have mising or unknown values in vector default is to say i dont know value (use na.rm)
mean_height <- mean(starwars$height, na.rm =TRUE)
mean_height
```

-   find and store standard deviation for character heights

```{r}
sd_height <- sd(starwars$height, na.rm =TRUE)
sd_height
```
